Analysing Constraint Grammars with a SAT-solver

### 2016-03-01 paper/lrec/problem_desc.tex
add another example of a use case

\begin{figure}[t]
\begin{center}

@@

\caption{Rules to select infinitive in Portuguese.}
\end{center}

\label{infrules}
\end{figure}

Given the rules in figure~\ref{infrules}, a grammar writer may ask the following questions while writing a grammar.

\begin{itemize}
\item Are all the rules distinct? (e.g. \texttt{Para} and \texttt{De} may be included in \texttt{Prep})
\item Can two or more rules be merged? (e.g. \texttt{SELECT Inf IF (-1C Prep OR Vai OR Vbmod ...)})
\item What is the best order for the rules?
\item Generate a sequence that triggers rules $R$ but not rules $R'$. 
\end{itemize}

@@

>>>>

\begin{figure}[t]
\centering

@@

\caption{Rules to select infinitive in Portuguese.}

\label{fig:infrules}
\end{figure}

Given the rules in figures~\ref{fig:infrules}~and~\ref{fig:regroup}, a
grammar writer may ask the following questions while writing a grammar.

\begin{itemize}
\item Are all the rules distinct? (e.g. \texttt{Para} and \texttt{De} may be included in \texttt{Prep})
\item Can two or more rules be merged? (e.g. \texttt{SELECT Inf IF
    (-1C Prep OR Vai OR Vbmod)})
\item Does my neat rewrite of a messy rule preserve the meaning?
\item What is the best order for the rules?
\item Generate a sequence that triggers rules $R$ but not rules $R'$ 
\end{itemize}

@@

\begin{figure}[t]
\centering
\begin{itemize}

\item[]\texttt{SELECT V + Prs/Imprt + Act + Neg}

\item[\texttt{IF}]
\begin{verbatim}(*-1C Negv LINK NOT *1 Vfin/PrsPrc/Inf) 
(NOT 0 N) (NOT 0 Pron) 
(NOT *1 Neg) (NOT *-1 Neg)
(NOT 0 Pass) (NOT *-1 Niin) 
(*-1C Negv LINK NOT *1 CLB?) 
(*-1C Negv LINK NOT 0 Imprt) ; 
\end{verbatim}

\item[\texttt{IF}]
\begin{verbatim}(NOT *-1 Niin OR Neg)  
(*-1C Negv
  LINK NOT 0 Imprt
  LINK NOT *1 Vfin/PrsPrc/Inf OR CLB?) 
(NOT 0 N OR Pron OR Pass) 
(NOT *1 Neg) ;
\end{verbatim}
\end{itemize}

\caption{Two versions of a condition in Finnish.}

\label{fig:regroup}
\end{figure}
